### 2012-04-09 trunk/tr-semanticsearchsurvey-data/intro.tex

%\begin{itemize}
%	\item 
	\textbf{Ambiguous Queries:} 
	Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought. Coming back to the example of product search, a user who is in the early stages of selection may not know exactly which product to look for. In this case, the user may name one or two characteristics of the product, such as \emph{cheap digital camera}. The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity. Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ an AND semantics between words, and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult. Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries. Lastly, users will try to find what they are looking for with the least possible words, adding additional terms after realizing that their original query was ambiguous. For example, when searching for people the user may type in a name, only to realize that there are multiple persons with the same name. Often, this is aggravated by the bias toward a single popular answer. For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name. \footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}.

@@

\subsection{Outline}
The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}. Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches. Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}. Then approaches are discussed along the subproblems of content interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}. After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}. Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, before we finally conclude in Section~\ref{sec:conclusion}.

>>>>

%\begin{itemize}
%	\item 
	\textbf{Ambiguous Queries:} 
	Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought. Coming back to the example of product search, a user who is in the early stages of selection may not know exactly which product to look for. In this case, the user may name one or two characteristics of the product, such as \emph{cheap digital camera}. The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity. Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ an AND semantics between words, and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult. Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries. Lastly, users will try to find what they are looking for with the least possible words, adding additional terms after realizing that their original query was ambiguous. For example, when searching for people the user may type in a name, only to realize that there are multiple persons with the same name. Often, this is aggravated by the bias toward a single popular answer. For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name.\footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}

@@

\subsection{Outline}
The paper is organized as follows: An overview of semantic search and the concepts it entails is presented in Section~\ref{sec:ss}. Then, the paper is organized mainly along the aspects based on which we distinguish different semantic search approaches. Different types of information needs, querying paradigms, data and semantic resources are presented in Section~\ref{sec:needs},~\ref{sec:querying},~\ref{sec:data} and ~\ref{sec:semantics}. Then approaches are discussed along the subproblems of data interpretation, query interpretation, matching and ranking in Section~\ref{sec:content},~\ref{sec:query},~\ref{sec:matching} and~\ref{sec:ranking}. After that, we present the main types of semantic search approaches and discuss their performances in Section~\ref{sec:approaches}. Main challenges derived from that and implications for future work are presented in Section~\ref{sec:challenges}, before we finally conclude in Section~\ref{sec:conclusion}.
